\newpage
\fancyhead[R]{12 November 2021}

Note that the cross-validation bandwidth from \Cref{thm:dalelane} is random. The kind of inequality in the the theorem is called \textbf{oracle inequality}, as it is not possible to obtain the values on each side. They involve the unknown $f_X\pa{x}$. The estimation of errors in cross-validation kernel estimation is hard, but in practice it often works well.

\subsection{Elements on the Fourier Transform}
A function is in $L^1\pa{\R}$ if $\int_{\R} \abs{f\pa{x}}dx <\infty$.
\begin{definition}
  If $f\in L^1\pa{\R}$, the Fourier transform of $f$ is defined for all $w\in \R$ by
  \begin{equation}
    \F\bra{f}\pa{w} = \int_\R e^{iwx} f\pa{x}dx.
  \end{equation}
\end{definition}
\begin{remark}
  The characteristic function of a random variable $X$ is
  \begin{equation}
    \varphi_X\pa{w} = \E\bra{e^{iwX}} = \int_\R e^{iwx} f_X\pa{x}dx.
  \end{equation}
\end{remark}
\begin{remark}\label{rem:fourier_l2}
  It is possible as well to define the Fourier transform of $f\in L^2\pa{\R}$. Therefore, we take a sequence $f_m \in L^1\pa{\R}\cap L^2\pa{\R}$ such that $\norm{f-f_m}^2_2\rightarrow 0$ as $m\rightarrow \infty$ and define the Fourier transform of $f$ as the $L^2$-limit of $\F \bra{f_m}$. More precisely, we may take $f_m\pa{x} = f\pa{x} \one_{\abs{x}\leq m}$. It is in $L^2$ as the product of an $L^2\pa{\R}$ function and a bounded function, and it is in $L^1\pa{\R}$ as a result of the Cauchy-Schwarz inequality:
  \begin{equation}
    \int_{\R} f\pa{x} \one_{\abs{x}\leq m} dx \leq \sqrt{\int_{\R} f\pa{x}^2 dx } \sqrt{\int_{-m}^m 1 dx } = \sqrt{2m}  \sqrt{\underbrace{\int_{\R} f\pa{x}^2 dx}_{<\infty} }.
  \end{equation}
  Moreover,
  \begin{equation}\label{eq:cauchy}
    \norm{f_m -f}^2_2 = \int_{-\infty}^m \abs{f\pa{x}}^2 dx + \int_m^\infty \abs{f\pa{x}}^2 dx \rightarrow 0
  \end{equation}
  as $m\rightarrow \infty$.
\end{remark}
\begin{exercise}
  If $f$ is symmetric, $\F \bra{f}$ is real-valued.
\end{exercise}

\begin{proposition}\label{prop:plancherel_inverse}
  If $f,\F\bra{f}\in L^2\pa{\R}\cap L^1\pa{\R}$, then
  \begin{enumerate}
  \item $\frac{1}{2\pi} \norm{\F\bra{f}}^2_2 = \norm{f}^2_2$ (Plancherel's theorem)
  \item For all $x\in \R$, $f\pa{x} = \frac{1}{2\pi} \int_\R e^{-iwx} \F\bra{f}\pa{w}dw$, the inversion of the Fourier transform.
  \end{enumerate}
\end{proposition}
\begin{proof}
  Omitted.
\end{proof}

\begin{remark}
  Back to remark \Cref{rem:fourier_l2}. By \cref{eq:cauchy}, for all $m,m', \norm{f_m -f_{m'}}_2^2\rightarrow 0$ as $m,m'\rightarrow \infty$, i.e.~$\pa{f_m}$ is a Cauchy sequence. By Plancherel's theorem,
  \begin{equation}
    \norm{\F \bra{f_m} -\F\bra{f_{m'}} }_2^2 = \norm{\F \bra{f_m -f_{m'} }}_2^2 = 2\pi \norm{f_m -f_{m'}}_2^2.
  \end{equation}
  Thus, $\F\bra{f_m}$ is a Cauchy sequence in $L^2\pa{\R}$, so that it admits a limit in $L^2\pa{\R}$, since $L^2\pa{\R}$ is a complete normed space. We can then define the Fourier transform of $f$ to be this limit.
\end{remark}
\begin{exercise}
 Prove
 \begin{enumerate}
   \item $\F\bra{f\pa{\cdot}} \pa{w} = a \F \bra{f\pa{\cdot}}\pa{w}$,
   \item $\F\bra{\frac{1}{h}f\pa{\frac{\pa{\cdot}}{h}}}\pa{w} = \F\bra{f\pa{\cdot}}\pa{hw}$,
   \item $\F\bra{f\pa{t-\cdot}}\pa{w} = e^{iwt} \F\bra{f\pa{\cdot}} \pa{-w}$.
 \end{enumerate}
\end{exercise}
\begin{exercise}
  If $\hat{f}_X$ is a kernel density estimator, where the kernel is symmetric, then
  \begin{enumerate}
    \item $\F\bra{K}$ is symmetric and real,
    \item $\F\bra{\hat{f}_X}\pa{w} = \phi_u \pa{w} \F\bra{K} \pa{hw}$,
  \end{enumerate}
  where $\phi_u \pa{w} = \frac{1}{n}\sum_{j=1}^n e^{iwX_j}$.
\end{exercise}
\begin{exercise}
  By 2 of \Cref{prop:plancherel_inverse}, check that the Fourier transform of the sinc kernel is $\one_{\abs{w}\leq 1}$.
\end{exercise}

Let $f\in L^1\pa{\R}$ such that $\F\bra{f}\in L^1\pa{\R}\cap L^2\pa{\R}$. Then
\begin{equation}
  f\pa{x} = \frac{1}{2\pi} \int_{\R} e^{-iwx}\F\bra{f}\pa{w} d w.
\end{equation}

We can define, after differentiating in the usual way without knowing whether the right-hand side is differentiable,
\begin{equation}
  f'\pa{x} \defeq \frac{i}{2\pi} \int_{\R} \pa{-iw} e^{-iwx} \F\bra{f}\pa{w}dw,
\end{equation}
and
\begin{equation}
  f''\pa{x} \defeq \frac{1}{2\pi} \int_\R \pa{w^2} e^{-iwx} \F\bra{f} \pa{w}dw,
\end{equation}
and so on. Building on this, we make the following definition.

\begin{definition}
  Let $\beta>0$, $L>0$, the Sobolev class $\calp_S\pa{\beta,L}$ is defined as
  \begin{equation}
    \calp_S\pa{\beta,L} = \set{f: f \text{ is a density on }  \R \text{ and } \int_{\R}\abs{w}^{2\beta} \abs{\F\bra{f}\pa{w}}^2 dw \leq 2\pi L^2}.
  \end{equation}
\end{definition}

\begin{remark}\label{rem:fourier_density_estimation}
  The Fourier transform is a useful tool in the measurement error model:
  \begin{equation}
    Y = X+ \varepsilon, \quad X\ci\varepsilon,
  \end{equation}
  only $Y$ is observed, $f_\varepsilon$ is known. The goal is to estimate $f_X$.
  \begin{equation}
    \E\bra{e^{itY}} = \E\bra{e^{iw\pa{X+\varepsilon}}} = \E\bra{e^{iwX}}\E\bra{e^{iw\varepsilon}}.
  \end{equation}
  Thus,
  \begin{equation}
  \phi_Y \pa{w} =  \phi_X\pa{w} \phi_{\varepsilon}\pa{w}.
  \end{equation}
  The Fourier transform maps convolutions to products. Thus,
  \begin{equation}
    \phi_X\pa{w} = \frac{\phi_Y\pa{w}}{\phi_{\varepsilon}\pa{w}}.
  \end{equation}
  The density of $X$ is therefore \textbf{nonparametrically identified}. We have
  \begin{equation}
    f_X\pa{x} = \frac{1}{2\pi} \int_{\R}e^{-iwx} \frac{\phi_Y\pa{w}}{\phi_{\varepsilon}\pa{w}}dw.
  \end{equation}
  One can build an estimator for the density of $X$ based on this, but the details are outside the scope of this course. An idea is
  \begin{equation}
    \hat{\phi}_Y\pa{w} =\frac{1}{n}\sum_{j=1}^m e^{iY_j w},
  \end{equation}
  and then
  \begin{equation}
    \hat{f}_X\pa{x} = \frac{1}{2\pi} \int_{-R}^R e^{-iwx} \frac{\hat{\phi}_Y\pa{x}}{\phi_{\varepsilon}\pa{x}}dx.
  \end{equation}
\end{remark}
